\documentclass[12pt]{article}
\usepackage{setspace}   % double spacing
\usepackage{geometry}   % margins 
\usepackage{hyperref}   % hyperlinks
% \usepackage{mathptmx} % times new roman
\usepackage{tocloft}    % table of contents
% ========================================== %
% document options
\doublespacing
\raggedright
\geometry{ 
    a4paper,
    margin=1in,
    lmargin=1.5in
}

% hyperlinks for toc
\usepackage{xcolor}
\hypersetup{
    colorlinks,
    linkcolor={red!50!black},
    citecolor={blue!50!black},
    urlcolor={blue!80!black}
}
% ========================================== %
% section notations
\renewcommand{\thesubsection}{\arabic{subsection}}
\renewcommand*\contentsname{ 
    {\MakeUppercase{Table of Contents}} 
}
\renewcommand*\listfigurename{ 
    {
        \section*{LIST OF FIGURES}
        \addcontentsline{toc}{section}{LIST OF FIGURES}
    } 
}
\renewcommand*\listtablename{
    {
        \section*{{LIST OF TABLES}}
        \addcontentsline{toc}{section}{LIST OF TABLES}
    } 
}
% ========================================== %
% custom variables
\newcommand{\thesistitle}{
    {\Large A comparative analysis of texture analysis methods on
ant head images}
}
\newcommand{\toppage}{\vspace*{0.3in}}
\newcommand{\chapterheader}[2]{
    \begin{center}
        \textbf{\Large{
            \section*{CHAPTER #1: #2}
            \addcontentsline{toc}{section}{CHAPTER #1: #2}
        }}
    \end{center}
}
% ========================================== %

\begin{document}
\pagenumbering{roman}
% ========================================== %
% thesis premable page
\toppage
\begin{center}
    \textbf{\MakeUppercase{\thesistitle}}
    \vspace{1in}

    A Thesis Presented to

    The Faculty of the Computer Science Department
    \vspace{1in}

    by
    \vspace{0.5in}

    Noah Gardner
    \vspace{1in}

    In Partial Fulfillment

    of Requirements for the Degree

    Master of Science in Computer Science

    \vspace{1in}
    Kennesaw State University

    May 2022
\end{center}
\thispagestyle{empty}
\newpage

% ========================================== %
% agreement
\toppage
\noindent In presenting this thesis as a partial fulfillment of the requirements
for an advanced degree from Kennesaw State University, I agree that the
university library shall make it available for inspection and circulation in
accordance with its regulations governing materials of this type. I agree that
permission to copy from, or to publish, this thesis may be granted by the
professor under whose direction it was written, or, in his absence, by the dean
of the appropriate school when such copying or publication is solely for
scholarly purposes and does not involve potential financial gain. It is
understood that any copying from or publication of, this thesis which involves
potential financial gain will not be allowed without written permission.
\vspace{2in}

\def\dotsign{\xleaders\hbox to .2em{\d{}}\hfill\d{}}
\begin{center}
    \makebox[.5\linewidth][r]\dotsign\smallskip\\
    Noah Gardner
\end{center}
\newpage

% ========================================== %
% notice to borrowers
\toppage
\begin{center}
    \textbf{\underline{Notice to Borrowers}}
\end{center}
\vspace{0.5in}

\noindent Unpublished theses deposited in the Library of Kennesaw State
University must be used only in accordance with the stipulations prescribed by
the author in the preceding statement.
\vspace{0.5in}

\noindent The author of this thesis is:
\begin{center}
    Noah Gardner

    1100 S Marietta Parkway

    Marietta, GA 30060
\end{center}

\noindent The director of this thesis is:
\begin{center}
    Chih-Cheng Hung

    1100 S Marietta Parkway

    Marietta, GA 30060
\end{center}
\vspace{0.5in}

\noindent Users of this thesis not regularly enrolled as students at Kennesaw
State University are required to attest acceptance of the preceding stipulations
by signing below. Libraries borrowing this thesis for the use of their patrons
are required to see that each user records here the information requested.
\vspace{0.3in}

\noindent
Name of user \hspace{0.2in} Address \hspace{0.2in} Date \hspace{0.2in} Type of
use (examination only or copying)
\newpage

% ========================================== %
% abstract preamble page title page
\toppage
\begin{center}
    \textbf{\MakeUppercase{\thesistitle}}
    \vspace{1in}

    An Abstract of

    A Thesis Presented to

    The Faculty of the Computer Science Department
    \vspace{1in}

    by
    \vspace{0.5in}

    Noah Gardner
    \vspace{1in}

    In Partial Fulfillment

    of Requirements for the Degree

    Master of Science in Computer Science

    \vspace{1in}
    Kennesaw State University

    May 2022
\end{center}
\newpage

% ========================================== %
% abstract page
\toppage
\begin{center}
    \section*{ABSTRACT}
    \addcontentsline{toc}{section}{ABSTRACT}
\end{center}
\vspace{0.5in}

\noindent There is a large variety of ant species, and most species are diverse
in terms of size, shape, behaviors, and especially skin (cuticle) textures.
However, the significance of ant cuticle texture is not widely researched. This
research employs modern machine learning methods such as texture analysis and
classification with CNN and clustering to automatically group similar ant
species to allow for the study of influences cuticle texture on ant ecology.
\newpage

% ========================================== %
% advisor preamble
\toppage
\begin{center}
    \textbf{\MakeUppercase{\thesistitle}}
    \vspace{1in}

    A Thesis Presented to

    The Faculty of the Computer Science Department
    \vspace{1in}

    by
    \vspace{0.5in}

    Noah Gardner
    \vspace{1in}

    In Partial Fulfillment

    of Requirements for the Degree

    Master of Science in Computer Science
    \vspace{0.5in}

    Advisor: Dr. Chih-Cheng Hung
    \vspace{0.5in}

    Kennesaw State University

    May 2022
\end{center}
\newpage

% ========================================== %
% dedication page
\vspace*{\fill}
\begin{center}
    \textit{To my family}
\end{center}
\vspace*{\fill}
\newpage

% ========================================== %
% quote page
\toppage
Never fail to have this attitude of mind, go forward without hurry, learn the
essence of things through frequent experiences, taking advantage of every
occasion. Fight against all kinds of people and be aware of their mind. Follow a
road that is a thousand leagues long one step at a time. Be without haste and be
convinced that all these practices are the duty of a bushi. Be victorious today
over what you were yesterday; tomorrow be victorious over your clumsiness and
then also over your skill. Practice in accordance with what I have written
without letting your mind deviate from the way.

\vspace{0.5in}
\hspace*{\fill} Miyamoto Musashi \footnote{Miyamoto Musashi, The Book of Five
    Rings}
\newpage

% ========================================== %
% acknowledgements page
\toppage
\begin{center}
    \section*{ACKNOWLEDGEMENTS}
    \addcontentsline{toc}{section}{ACKNOWLEDGEMENTS}
\end{center}
\vspace{0.5in}

\noindent I would like to thank my loving family for their support throughout
the completion of my graduate degree. I would also like to thank Dr. Chih-Cheng
Hung for his mentorship for my thesis, for his guidance in my other research
projects, and for giving me the freedom to explore a variety of research topics.
\newpage

% ========================================== %
% table of contents
\begin{center}
    \tableofcontents
\end{center}
\newpage

% ========================================== %
% list of figures
\begin{center}
    \listoffigures
\end{center}
\newpage

% ========================================== %
% list of tables 
\begin{center}
    \listoftables
\end{center}
\newpage

% ========================================== %
% begin content
\pagenumbering{arabic}
\chapterheader{1}{INTRODUCTION AND BACKGROUND}
\subsection{Introduction}

\end{document}